### 2023-01-14 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@d250e92aa9612d39e1283c22025bf6fb78863610 🚀
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@114806505e9b51e115f1faeaff195f84a965611d 🚀
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@cc38d6bfa2362a09493e9a46979610d8934b75b7 🚀

\usepackage{lineno}
\usepackage[nolists,noheads]{endfloat}

@@

Here, we illustrate how our confidence that a pair of species never
interacts highly depends on sampling effort. We suggest that surveys of
species interactions can benefit from simulation modeling of the
sampling process. We demonstrate how the realized false-negative-rate of
interactions is related to the relative abundance of the species pool,
and introduce a method to produce a null estimate of the
false-negative-rate given total sampling effort (the total count of all
interactions seen among all species-pairs) and a method for including
uncertainty into model predictions of interaction probabilities to
account for observation error. We then show that positive associations
in co-occurrence data can increase the realized number of
false-negatives, and demonstrate these positive associations are rampant
in network datasets, and conclude by recommending that the simulation of
sampling effort and species occurrence can and should be used to help
design surveys of species interaction diversity (Moore \& McCarthy
2016), and by advocating use of null models like those presented here as
a tool for both guiding design of surveys of species interactions and
for modeling detection error in predictive models.

@@

There is also an analytic way to approximate this distribution using the
normal approximation to binomial. As a reminder, as the total number of
samples \(n\) from a binomial distribution with success probability
\(p\) from approaches infinity, the sum of total successes across all
samples approaches a normal distribution with mean \(np\) and variance
\(np(1-p)\). We can use this to correct the estimate \(p_{ij}\) based on
the expected false-negative-rate \(p_{fn}\) and false-positive rate
\(p_{fp}\) to obtain the limiting distribution as the number of
resamples approaches infinity for the resampled \(p_{ij}^*\) for a given
number of particles \(n_p\). We do this by first adjusting for the rates
of observation error to get the mean resampled probability,
\(\mathbb{E}[{p_{ij}^*}]\), as

>>>>

\usepackage{lineno}
% \usepackage[nolists,noheads]{endfloat}

\usepackage{floatrow}

\floatsetup[figure]{
              floatwidth=\textwidth}

@@

Here, we illustrate how our confidence that a pair of species never
interacts highly depends on sampling effort. We demonstrate how the
realized false-negative-rate of interactions is related to the relative
abundance of the species pool, and introduce a method to produce a null
estimate of the false-negative-rate given total sampling effort (the
total count of all interactions seen among all species-pairs) and a
method for including uncertainty into model predictions of interaction
probabilities to account for observation error. We then confront these
models with data, by showing that positive associations in co-occurrence
data can increase the realized number of false-negatives and by showing
these positive associations are rampant in network datasets. We conclude
by recommending that the simulation of sampling effort and species
occurrence can and should be used to help design surveys of species
interaction diversity (Moore \& McCarthy 2016), and by advocating use of
null models like those presented here as a tool for both guiding design
of surveys of species interactions and for including detection error
into predictive models.

@@

There is also an analytic way to approximate this distribution using the
normal approximation to binomial. As a reminder, as the total number of
samples \(N\) from a binomial distribution for \(n\) trials with success
probability \(p\) from approaches infinity, the sum of total successes
across all samples approaches a normal distribution with mean \(np\) and
variance \(np(1-p)\). We can use this to correct the estimate \(p_{ij}\)
based on the expected false-negative-rate \(p_{fn}\) and false-positive
rate \(p_{fp}\) to obtain the limiting distribution as the number of
resamples approaches infinity for the resampled \(p_{ij}^*\) for a given
number of particles \(n_p\). We do this by first adjusting for the rates
of observation error to get the mean resampled probability,
\(\mathbb{E}[{p_{ij}^*}]\), as
